Supplement: Analysis and code for 'Testing Perceptual Accuracy in Charts using Surveys

### 2023-07-21 analysis/analysis.qmd
comparison to floating bars
floating bars

round_35 %>% 
  mutate(
    response3 = c("Wrong", "They are the same", "Correct")[correct+not_wrong+1],
    response3 = factor(response3, levels=rev(c("Correct", "They are the same", "Wrong")))
  ) %>% 
  ggplot(aes(x = task)) + 
  geom_bar(aes(fill = response3, weight = weight), position="fill") +
#  facet_grid(.~task) + 
  theme(legend.position="bottom") + 
  scale_fill_manual("Response", values=c("orange", "grey", "steelblue")) +
  xlab("") +
  scale_y_continuous("Percent responses", breaks=seq(0,1,by=0.25), labels = 100*seq(0,1,by=0.25)) + 
  geom_rect(
    aes(
      xmin = as.numeric(task) - 0.45,
      ymin = inv_logit(estimate - 1.96* std.error),
      xmax = as.numeric(task) + 0.45,
      ymax = inv_logit(estimate + 1.96* std.error),
    ), 
    fill = "black", alpha = 0.25, #colour = "white", linewidth = 0.25,
    data = coefs_35_correct
  ) +
  geom_segment(
    aes(
      x = as.numeric(task) - 0.45,
      y = inv_logit(estimate ),
      xend = as.numeric(task) + 0.45,
      yend = inv_logit(estimate )
    ), 
    alpha = 1, colour = "black", linewidth = 0.25,
    data = coefs_35_correct
  ) +
  geom_rect(
    aes(
      xmin = as.numeric(task) - 0.45,
      ymin = inv_logit(estimate - 1.96* std.error),
      xmax = as.numeric(task) + 0.45,
      ymax = inv_logit(estimate + 1.96* std.error),
    ), 
    fill = "black", alpha = 0.25, #colour = "white", linewidth = 0.25,
    data = coefs_35_notwrong
  ) +
  geom_segment(
    aes(
      x = as.numeric(task) - 0.45,
      y = inv_logit(estimate ),
      xend = as.numeric(task) + 0.45,
      yend = inv_logit(estimate )
    ), 
    alpha = 1, colour = "black", linewidth = 0.25,
    data = coefs_35_notwrong
  )
#+ 
#  geom_text(aes(label=letters), y = -0.05, data = ci_confint, colour = "steelblue") +
#  geom_text(aes(label=letters), y = 1.05, data = ci_confint3, colour = "darkorange")

>>>>

round_35 %>% 
  mutate(
    response3 = c("Wrong", "They are the same", "Correct")[correct+not_wrong+1],
    response3 = factor(response3, levels=rev(c("Correct", "They are the same", "Wrong")))
  ) %>% 
  ggplot(aes(x = task)) + 
  geom_bar(aes(fill = response3, weight = weight), position="fill") +
#  facet_grid(.~task) + 
  theme(legend.position="bottom") + 
  scale_fill_manual("Response", values=c("orange", "grey", "steelblue")) +
  xlab("") +
  scale_y_continuous("Percent responses", breaks=seq(0,1,by=0.25), labels = 100*seq(0,1,by=0.25)) + 
  geom_rect(
    aes(
      xmin = as.numeric(task) - 0.45,
      ymin = inv_logit(estimate - 1.96* std.error),
      xmax = as.numeric(task) + 0.45,
      ymax = inv_logit(estimate + 1.96* std.error),
    ), 
    fill = "black", alpha = 0.25, #colour = "white", linewidth = 0.25,
    data = coefs_35_correct
  ) +
  geom_segment(
    aes(
      x = as.numeric(task) - 0.45,
      y = inv_logit(estimate ),
      xend = as.numeric(task) + 0.45,
      yend = inv_logit(estimate )
    ), 
    alpha = 1, colour = "black", linewidth = 0.25,
    data = coefs_35_correct
  ) +
  geom_rect(
    aes(
      xmin = as.numeric(task) - 0.45,
      ymin = inv_logit(estimate - 1.96* std.error),
      xmax = as.numeric(task) + 0.45,
      ymax = inv_logit(estimate + 1.96* std.error),
    ), 
    fill = "black", alpha = 0.25, #colour = "white", linewidth = 0.25,
    data = coefs_35_notwrong
  ) +
  geom_segment(
    aes(
      x = as.numeric(task) - 0.45,
      y = inv_logit(estimate ),
      xend = as.numeric(task) + 0.45,
      yend = inv_logit(estimate )
    ), 
    alpha = 1, colour = "black", linewidth = 0.25,
    data = coefs_35_notwrong
  ) +
  ggtitle("Comparison of unaligned tiles")
#+ 
#  geom_text(aes(label=letters), y = -0.05, data = ci_confint, colour = "steelblue") +
#  geom_text(aes(label=letters), y = 1.05, data = ci_confint3, colour = "darkorange")

```{r m35-summary}
